---
output: html_document
runtime: shiny
---
---

Title: "Statistical & Supply Chain Analytics Dashboard"
output:
flexdashboard::flex_dashboard:
orientation: rows
vertical_layout: fill
theme: darkly
runtime: shiny
--------------

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(DT)
library(lubridate)
library(shiny)
library(corrplot)
library(forecast)
library(randomForest)

amazon_sales_dataset <- read_csv("amazon_sales_dataset.csv")

amazon_sales_dataset$order_month <- month(amazon_sales_dataset$order_date, label = TRUE)
```

# Analysis {.tabset}

## Distribution Analysis

```{r}
renderPlotly({

p <- ggplot(amazon_sales_dataset,
aes(total_revenue))+
geom_histogram(bins=30,fill="steelblue")+
theme_minimal()

ggplotly(p)

})
```

## Time Series Trend

```{r}
renderPlotly({

trend <- amazon_sales_dataset %>%
group_by(order_month) %>%
summarise(revenue=sum(total_revenue))

p <- ggplot(trend,
aes(order_month,revenue,group=1))+
geom_line(size=1,color="cyan")+
geom_point()+
theme_minimal()

ggplotly(p)

})
```

## Regression Analysis

```{r}
renderPlotly({

p <- ggplot(amazon_sales_dataset,
aes(discount_percent,total_revenue))+
geom_point(alpha=0.5,color="orange")+
geom_smooth(method="lm",color="red")+
theme_minimal()

ggplotly(p)

})
```

## Regression Model Output

```{r}
model <- lm(total_revenue ~ price + discount_percent + quantity_sold + rating,
data=amazon_sales_dataset)

datatable(summary(model)$coefficients)
```

## ANOVA Test

```{r}
anova_model <- aov(total_revenue ~ product_category,
data=amazon_sales_dataset)

datatable(summary(anova_model)[[1]])
```

## P-Value Analysis

```{r}
pvals <- summary(model)$coefficients[,4]

datatable(data.frame(P_Value=pvals))
```

## Z-Score Outlier Detection

```{r}
z <- scale(amazon_sales_dataset$total_revenue)

outliers <- amazon_sales_dataset[abs(z)>3,]

datatable(head(outliers,20))
```

## Correlation Heatmap

```{r}
num_data <- amazon_sales_dataset %>%
select(price,discount_percent,quantity_sold,rating,review_count,total_revenue)

cor_matrix <- cor(num_data)

plot_ly(
z=cor_matrix,
x=colnames(cor_matrix),
y=rownames(cor_matrix),
type="heatmap",
colors=colorRamp(c("red","black","green"))
)
```

## Demand Forecasting (ARIMA)

```{r}
monthly <- amazon_sales_dataset %>%
group_by(order_month) %>%
summarise(revenue=sum(total_revenue))

ts_data <- ts(monthly$revenue)

fit <- auto.arima(ts_data)

forecast_data <- forecast(fit, h=6)

renderPlotly({

p <- autoplot(forecast_data)

ggplotly(p)

})
```

## Inventory Turnover Analytics

```{r}
inventory <- amazon_sales_dataset %>%
group_by(product_category) %>%
summarise(
revenue=sum(total_revenue),
units=sum(quantity_sold)
)

inventory$turnover <- inventory$revenue / inventory$units

renderPlotly({

p <- ggplot(inventory,
aes(product_category,turnover,fill=product_category))+
geom_bar(stat="identity")+
theme_minimal()

ggplotly(p)

})
```

## Feature Importance Model

```{r}
rf_model <- randomForest(
total_revenue ~ price + discount_percent + quantity_sold + rating + review_count,
data=amazon_sales_dataset,
importance=TRUE
)

importance_df <- data.frame(
Feature=row.names(importance(rf_model)),
Importance=importance(rf_model)[,1]
)

renderPlotly({

p <- ggplot(importance_df,
aes(reorder(Feature,Importance),Importance))+
geom_bar(stat="identity",fill="cyan")+
coord_flip()+
theme_minimal()

ggplotly(p)

})
```

## Hypothesis Testing

```{r}
high_discount <- amazon_sales_dataset$total_revenue[
amazon_sales_dataset$discount_percent > 20]

low_discount <- amazon_sales_dataset$total_revenue[
amazon_sales_dataset$discount_percent <= 20]

test <- t.test(high_discount,low_discount)

datatable(data.frame(
Statistic=test$statistic,
P_Value=test$p.value
))
```

## Statistical Summary

```{r}
datatable(summary(amazon_sales_dataset))
```
